### 2019-07-16 manuscript/methods.tex
edits to "model comparison key questions"
In Results, moved the Q/A section to before Pathways, because the
questions are mostly about diversification.

Using the marginal likelihood values, we calculated Bayes factors to argue five key biological and methodological questions:
\begin{enumerate}
\item Are diversification patterns only determined by hidden states and not the traits of interest?- Comparison of character independent models against hidden state (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
\item Are hidden state necessary to add in this context?- Comparison of simple models against hidden state models (\cref{supptable:testaddhidden}).
\item Is a second trait adding information to the diversification process?- Comparison of lumped models against IC/CD/CP models (\cref{figure:lumped,table:lumped}).
\item Is there evidence for diploidization?- Comparison amongst models with and without diploidization (\cref{suppfigure:alldip,supptable:testdiploidization}).
\item Do asymmetrical rates in the model affect the pattern of diversification? - Comparison amongst hidden states models with equal hidden rates and asymmetrical rates (\cref{suppfigure:asymmetric,supptable:asymmetry}).
\end{enumerate}

Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $K=ln(BF(M_1,\ M_0)) = \ln[ P(\mathbf{X} | M_1) - P(\mathbf{X} | M_0)]$.
There is `strong evidence'  for $M_1$ when this value is more than 10, moderate support if the value is more than 1 and no evidence if the value is between -1 and 1. If the vaue of  $K$ is negative the evidence goes towards $M_0$.  \citep{kass1995}.

>>>>

Using the marginal likelihood values, we calculated Bayes factors to argue five key biological and methodological questions:
\begin{enumerate}
\item Are diversification patterns only determined by hidden states and not the traits of interest?---Comparison of character independent models against hidden state (\cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
\item Are hidden states necessary to explain diversification rate heterogeneity?---Comparison of simple models against hidden state models (\cref{supptable:testaddhidden}).
\item Does a second focal trait add information about the diversification process?---Comparison of lumped models against IC/CD/CP models (\cref{figure:lumped,table:lumped}).
\item Are conclusions robust to assumptions about hidden state transitions?---Comparison amongst hidden states models with equal hidden rates and asymmetrical rates (\cref{suppfigure:asymmetric,supptable:asymmetry}).
\item Is there evidence for diploidization?---Comparison amongst models with and without diploidization (\cref{suppfigure:alldip,supptable:testdiploidization}).
\end{enumerate}

Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $K=ln(BF(M_1,\ M_0)) = \ln[ P(\mathbf{X} | M_1) - P(\mathbf{X} | M_0)]$.
There is `strong evidence' for $M_1$ when this value is more than 10, moderate support if the value is more than 1, and no evidence if the value is between -1 and 1.
If the value of $K$ is negative the evidence goes towards $M_0$ \citep{kass1995}.

### 2019-07-16 manuscript/results.tex
edits to "model comparison key questions"
In Results, moved the Q/A section to before Pathways, because the
questions are mostly about diversification.

@@

\subsection{Model selection key questions}

\subsubsection{Are diversification patterns only determined by hidden states?}
Whether the determination of the diversification is dependent on the focal traits and not only on the hidden state was done via the comparisons of character independent models against the focal traits w/o hidden states models (results shown in  \cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
The general pattern is to moderate- to strongly prefer models with focal traits and asymmetric hidden states over the rest of the models with the exception of the ploidy only model where the character independent model (M2) seems to be equally preferred($K=0.5$) as the model with ploidy and asymmetric hidden rates (M4, \cref{table:bayesfactors}).

\subsubsection{Are hidden states necessary?}
In the comparisons of simple diversification models of focal traits against models with hidden states we found that models with asymmetric hidden traits are strongly preferred over simpler models (summarized in table \cref{supptable:testaddhidden}).

\subsubsection{Is a second trait adding information to the diversification process?}
As summarized in  \cref{table:lumped}, it is moderately preferred to add breeding system to ploidy only models (\cref{suppfigure:lumpedDP}).
When adding ploidy information to breeding system models to create a three-state model, we found that there is no evidence that it is preferred (M28 vs. M16 \cref{suppfigure:lumpedIC}B and C). 
However, it becomes moderately preferable in the presence of hidden states (M29 vs. M23  \cref{suppfigure:lumpedIC}E and C).

\subsubsection{Is there evidence for diploidization?}
We considered models both with and without diploidization in order to explore its effects on the estimates of state-dependent diversification.
For the models that only include diploid and polyploid states (M6-M10) the results are similar in terms of the effect of diversification (\cref{suppfigure:alldip}).
When comparing models with diploidization against models without diploidization we found moderate evidence that models containing the parameter $\delta$ are preferred over models without diploidization (summarized in \cref{supptable:testdiploidization}).

\subsubsection{Do asymmetric rates in hidden states models affect the pattern of diversification?}
When comparing different types of asymmetry across hidden states models we found that the asymmetry did not change the direction of effects in net diversification results . However, models with asymmetric hidden rates reduced the overlap amongst net diversification posterior distributions as shown in \cref{suppfigure:asymmetric}. Furthermore, hidden state models with asymmetric traits are strongly preferred over models with equal rates between hidden states (summarized in \cref{supptable:asymmetry}).

>>>>

\subsection{Key questions about diversification and transitions}

The above results include several of our statistical model comparison findings.
Here we return to the five specific questions we targeted with our model comparisons.

\begin{enumerate}

    \item Are diversification patterns only determined by hidden states and not the traits of interest?
    No, our focal traits are supported as having associations with diversification differences.
    In most cases, we find moderate to strong preference for models with the focal traits as well as hidden states, over models with only hidden states \cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).

    \item Are hidden states necessary to explain diversification rate heterogeneity?
    Yes, models with hidden states that influence diversification are strongly preferred over models containing only the focal traits (\cref{supptable:testaddhidden}).
    This means that there are potentially many sources of diversification shifts within the family.

    \item Does a second focal trait add information about the diversification process?
    Yes, in most cases models with both ploidy and breeding system are preferred over models with only one of the focal traits (\cref{table:lumped,suppfigure:lumpedDP,suppfigure:lumpedIC}).

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates \cref{suppfigure:asymmetric}.

    \item Is there evidence for diploidization?
    Perhaps: when comparing models with diploidization against models without it, we found moderate evidence that models containing diploidization are preferred (\cref{supptable:testdiploidization}).
    We discuss later some further challenges in identifying diploidization.
    We further found that our main conclusions about net diversification differences are not dependent on whether diploidization in included (\cref{suppfigure:alldip}).

\end{enumerate}

@@

%--------------------------------------------------
% \subsection{Model selection key questions}
% 
% \subsubsection{Are diversification patterns only determined by hidden states?}
% Whether the determination of the diversification is dependent on the focal traits and not only on the hidden state was done via the comparisons of character independent models against the focal traits w/o hidden states models (results shown in  \cref{table:bayesfactors,table:M11M15,supptable:M6M10,supptable:M16M20,supptable:M21M25}).
% The general pattern is to moderate- to strongly prefer models with focal traits and asymmetric hidden states over the rest of the models with the exception of the ploidy only model where the character independent model (M2) seems to be equally preferred($K=0.5$) as the model with ploidy and asymmetric hidden rates (M4, \cref{table:bayesfactors}).
% 
% \subsubsection{Are hidden states necessary?}
% In the comparisons of simple diversification models of focal traits against models with hidden states we found that models with asymmetric hidden traits are strongly preferred over simpler models (summarized in table \cref{supptable:testaddhidden}).
% 
% \subsubsection{Is a second trait adding information to the diversification process?}
% As summarized in  \cref{table:lumped}, it is moderately preferred to add breeding system to ploidy only models (\cref{suppfigure:lumpedDP}).
% When adding ploidy information to breeding system models to create a three-state model, we found that there is no evidence that it is preferred (M28 vs. M16 \cref{suppfigure:lumpedIC}B and C). 
% However, it becomes moderately preferable in the presence of hidden states (M29 vs. M23  \cref{suppfigure:lumpedIC}E and C).
% 
% \subsubsection{Is there evidence for diploidization?}
% We considered models both with and without diploidization in order to explore its effects on the estimates of state-dependent diversification.
% For the models that only include diploid and polyploid states (M6-M10) the results are similar in terms of the effect of diversification (\cref{suppfigure:alldip}).
% When comparing models with diploidization against models without diploidization we found moderate evidence that models containing the parameter $\delta$ are preferred over models without diploidization (summarized in \cref{supptable:testdiploidization}).
% 
% \subsubsection{Do asymmetric rates in hidden states models affect the pattern of diversification?}
% When comparing different types of asymmetry across hidden states models we found that the asymmetry did not change the direction of effects in net diversification results . However, models with asymmetric hidden rates reduced the overlap amongst net diversification posterior distributions as shown in \cref{suppfigure:asymmetric}. Furthermore, hidden state models with asymmetric traits are strongly preferred over models with equal rates between hidden states (summarized in \cref{supptable:asymmetry}).
%--------------------------------------------------
